Evaluation of a Cache-Oblivious Data Structure [draft-2]

### 2008-06-02 paper/paper.tex
Changed plots and figures so all plots fit on a single page.

\usepackage{pslatex}
\usepackage{epsfig}
\usepackage{appendix}
\usepackage{float}
\usepackage{url}

@@

\begin{program}[t]
\begin{verbatim}
Queue queue = new Queue;
Set generated = new Set;
queue.insert(initial_state);
while (!queue.empty()) {
    State state = queue.extract();
    for (State s : successors(state)) {
        if (generated.contains(s) == false) {
            generated.insert(s);
            queue.insert(s);
        }
    }
}
\end{verbatim}
\caption{Pseudo-code for a simple state search algorithm.}
\label{prog-search}
\end{program}

@@

\begin{figure}[t]
\centering
\includegraphics[width=83mm]{hash-table}
\caption{A depiction of a separate-chaining hash table}
\label{fig-hash-table}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[width=83mm]{b-tree}
\caption{A depiction of a B-tree}
\label{fig-b-tree}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=83mm]{bender-set}
\caption{A depiction of a Bender set}
\label{fig-bender-set}
\end{figure}

@@

Now that we have established the parameters to use for the other test cases,
we can run final experiments on all three test cases.
The execution times for these cases are presented in figures
\ref{fig-eratosthenes_wctime}--\ref{fig-peterson_wctime}
and the corresponding memory usage is presented in
figures \ref{fig-eratosthenes_vss}--\ref{fig-peterson_vss}.

@@

%\begin{figure}
%\centering
%\includegraphics[width=83mm]{fig-queuesize}
%\caption{Queue size}
%\label{fig-quesize}
%\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=83mm]{fig-transitions}
%\caption{Transitions}
%\label{fig-transitions}
%\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes-hash_wctime}
\caption{Execution time of hash table on Eratosthenes}
\label{fig-eratosthenes-hash_wctime}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes-btree_wctime}
\caption{Execution time of B-tree on Eratosthenes}
\label{fig-eratosthenes-btree_wctime}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes-bender_wctime}
\caption{Execution time of Bender set on Eratosthenes}
\label{fig-eratosthenes-bender_wctime}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes-hash_vss}
\caption{Memory usage of hash table on Eratosthenes}
\label{fig-eratosthenes-hash_vss}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes-btree_vss}
\caption{Memory usage of B-tree on Eratosthenes}
\label{fig-eratosthenes-btree_vss}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes-bender_vss}
\caption{Memory usage of Bender set on Eratosthenes}
\label{fig-eratosthenes-bender_vss}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes_wctime}
\caption{Execution time on Eratosthenes}
\label{fig-eratosthenes_wctime}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-leader2_wctime}
\caption{Execution time on Leader2}
\label{fig-leader2_wctime}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-peterson_wctime}
\caption{Execution time on Peterson\_N}
\label{fig-peterson_wctime}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-eratosthenes_vss}
\caption{Memory usage on Eratosthenes}
\label{fig-eratosthenes_vss}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-leader2_vss}
\caption{Memory usage on Leader2}
\label{fig-leader2_vss}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=83mm]{fig-peterson_vss}
\caption{Memory usage on Peterson\_N}
\label{fig-peterson_vss}
\end{figure}

>>>>

\usepackage{pslatex}
\usepackage{epsfig}
\usepackage{appendix}
\usepackage{float}
\usepackage{url}
\usepackage{subfigure}

@@

\begin{program}[t]
\begin{verbatim}
Queue queue = new Queue;
Set generated = new Set;
queue.insert(initial_state);
while (!queue.empty()) {
    State state = queue.extract();
    for (State s : successors(state)) {
        if (generated.contains(s) == false) {
            generated.insert(s);
            queue.insert(s);
        }
    }
}
\end{verbatim}
\caption{Pseudo-code for a simple state search algorithm}
\label{prog-search}
\end{program}

@@

\begin{figure}[t]
\centering
\includegraphics[width=83mm]{hash-table}
\caption{Depiction of a separate-chaining hash table}
\label{fig-hash-table}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[width=83mm]{b-tree}
\caption{Depiction of a B-tree}
\label{fig-b-tree}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=83mm]{bender-set}
\caption{Ddepiction of a Bender set}
\label{fig-bender-set}
\end{figure}

@@

Now that we have established the parameters to use for the other test cases,
we can run final experiments on all three test cases.
The execution times for these cases are presented in Figure \ref{fig-wctime}
and the corresponding memory usage is presented in Figure \ref{fig-vss}.

@@

\begin{figure*}[p]
\centering
\subfigure[B-tree]{
    \label{fig-eratosthenes-hash_wctime}
    \includegraphics[width=56mm]{fig-eratosthenes-hash_wctime}}
\subfigure[Hash table]{
    \label{fig-eratosthenes-btree_wctime}
    \includegraphics[width=56mm]{fig-eratosthenes-btree_wctime}}
\subfigure[Bender set]{
    \label{fig-eratosthenes-bender_wctime}
    \includegraphics[width=56mm]{fig-eratosthenes-bender_wctime}}
\caption{Execution times per data structure on Eratosthenes}
\label{fig-eratosthenes-wctime}
\end{figure*}

\begin{figure*}[p]
\centering
\subfigure[B-tree]{
    \label{fig-eratosthenes-hash_vss}
    \includegraphics[width=56mm]{fig-eratosthenes-hash_vss}}
\subfigure[Hash table]{
    \label{fig-eratosthenes-btree_vss}
    \includegraphics[width=56mm]{fig-eratosthenes-btree_vss}}
\subfigure[Bender set]{
    \label{fig-eratosthenes-bender_vss}
    \includegraphics[width=56mm]{fig-eratosthenes-bender_vss}}
\caption{Memory usage per data structure on Eratosthenes}
\label{fig-eratosthenes-vss}
\end{figure*}

\begin{figure*}[p]
\centering
\subfigure[Eratosthenes]{
    \label{fig-eratosthenes_wctime}
    \includegraphics[width=56mm]{fig-eratosthenes_wctime}}
\subfigure[Leader2]{
    \label{fig-leader2_wctime}
    \includegraphics[width=56mm]{fig-leader2_wctime}}
\subfigure[Peterson\_N]{
    \label{fig-peterson_wctime}
    \includegraphics[width=56mm]{fig-peterson_wctime}}
\caption{Execution times per test case}
\label{fig-wctime}
\end{figure*}

\begin{figure*}[p]
\centering
\subfigure[Eratosthenes]{
    \label{fig-eratosthenes_vss}
    \includegraphics[width=56mm]{fig-eratosthenes_vss}}
\subfigure[Leader2]{
    \label{fig-leader2_vss}
    \includegraphics[width=56mm]{fig-leader2_vss}}
\subfigure[Peterson\_N]{
    \label{fig-peterson_vss}
    \includegraphics[width=56mm]{fig-peterson_vss}}
\caption{Memory usage per test case}
\label{fig-vss}
\end{figure*}
